A pub-sub mechanism for Cardano and Plutus

### 2019-03-14 paper.tex
Cleaning up references

\begin{abstract}
  On this paper we demonstrate how we can use DataScripts to communicate different programs using the Cardano Blockchain and the Plutus Smart Contract programming language. We construct a mechanism that works in a way akin to a pub-sub communication system.
\end{abstract}

@@

\section{Introduction}
Blockchains provide a new way to intercommunicate different actors in the world. The blockchains provide a solution for the old problem of getting to cooperate different actors that may not want to cooperate. In this sense, the main use of the Blockchain has been so far as a ledger that is mostly handled manually. When two actors want to communicate, they use mostly manual approaches (such as chats, videoconferences, or plain old phone calls) before actually using the Blockchain, in most cases as a ledger for paying.

In order to be able to automate some of this manual communication, an automatic way of communicating these actors shall be developed, so that the actors can communicate without resorting to manual ways.

@@

And we continue with functions for extracting specific fields in our \verb|Foo| datastructure:
\nopagebreak
\begin{verbatim}
getFooBar ::
  DataScript ->
  Maybe Int
getFooBar datascript =
    getInt $ evaluateCekTrace (unsafeCoerce (accessor `applyScript` datascript)
  where
    accessor = fooBarAccessor

@@

instance Unlift Int where
  unlift (DataScript ds) = fromIntegral <$> (getInt $ evaluateCekTrace (unsafeCoerce ds))
\end{verbatim}

@@

\begin{verbatim}
instance Unlift PubKey where
  unlift (DataScript ds) = PubKey <$> unlift (DataScript (extractor `applyScript` ds))
    where
      extractor = $$(Ledger.compileScript [|| \(PubKey x) -> x ||])
\end{verbatim}

@@

%\bibitem{lamport94}
%  Leslie Lamport,
%    \textit{\LaTeX: a document preparation system},
%    Addison Wesley, Massachusetts,
%    2nd edition,
%    1994.

%\bibitem{bl}Business Logic layer, \url{http://en.wikipedia.org/wiki/Business_logic_layer}, 23 12 2011.

\bibitem{plutus-core-constant}
  Plutus Core Constant datatype,
    \url{https://github.com/input-output-hk/plutus/blob/master/language-plutus-core/src/Language/PlutusCore/Type.hs#L235},

\bibitem{plutus-core-term}
  Plutus Core Term datatype,
    \url{ https://github.com/input-output-hk/plutus/blob/master/language-plutus-core/src/Language/PlutusCore/Type.hs#L244},

\bibitem{address-map}
  Wallet API Address Map, \url{https://github.com/input-output-hk/plutus/blob/master/wallet-api/src/Wallet/Emulator/AddressMap.hs#L39}

\bibitem{outboros}
  Outboros Proof of Stake, \url{https://cardanodocs.com/cardano/proof-of-stake/}

\bibitem{plutus-playground}
  Plutus Playground, \url{https://prod.playground.plutus.iohkdev.io/}

\bibitem{plutus-emulator}
  Plutus Emulator, \url{https://github.com/input-output-hk/plutus/tree/master/wallet-api/src/Wallet/Emulator}

>>>>

\begin{abstract}
  On this paper we demonstrate how we can use DataScripts to communicate different programs using the Cardano Blockchain and the Plutus Smart Contract programming language. We construct a mechanism that works in a way akin to a pub-sub communication system. This mechanism has been developed during the development of the GiG Economy Token\cite{gig-token}.
\end{abstract}

@@

\section{Introduction}
Blockchains provide a new way to intercommunicate different actors in the world. The blockchains provide a solution for the old problem of getting to cooperate different actors that may not want to cooperate. In this sense, the main use of the Blockchain has been so far as a ledger that is mostly handled manually. When two actors want to communicate, they use manual approaches (such as chats, videoconferences, or plain old phone calls) before actually using the Blockchain, in most cases as a ledger for payment.

In order to be able to automate some of this manual communication, an automatic way of communicating these actors shall be developed, so that the actors can communicate without resorting to manual ways. The GiG Economy Token\cite{gig-token} uses this mechanism to communicate freelancers and employers prior to actually dealing with the payment details.

@@

And we continue with functions for extracting specific fields in our \verb|Foo| datastructure:
\nopagebreak
\begin{verbatim}
getFooBar ::
  DataScript ->
  Maybe Int
getFooBar datascript = getInt r
  where
    r = evaluateCekTrace (unsafeCoerce (accessor `applyScript` datascript)
    accessor = fooBarAccessor

@@

instance Unlift Int where
  unlift (DataScript ds) = fromIntegral <$> i
    where
      i = getInt $ evaluateCekTrace (unsafeCoerce ds)
\end{verbatim}

@@

\begin{verbatim}
instance Unlift PubKey where
  unlift (DataScript ds) = PubKey <$> pk
    where
      pk = unlift (DataScript (extractor `applyScript` ds))
      extractor = $$(Ledger.compileScript [|| \(PubKey x) -> x ||])
\end{verbatim}

@@

\bibitem{gig-token}
  GiG Economy Token organization at GitHub, \newline
    \url{https://github.com/gig-economy-token}.

\bibitem{outboros}
  Outboros Proof of Stake, \newline
    \url{https://cardanodocs.com/cardano/proof-of-stake/}.

\bibitem{plutus-emulator}
  Plutus Emulator, \newline
    \url{https://github.com/input-output-hk/plutus/tree/master/wallet-api/src/Wallet/Emulator}.

\bibitem{plutus-playground}
  Plutus Playground, \newline
    \url{https://prod.playground.plutus.iohkdev.io/}.

\bibitem{plutus-core-constant}
  Plutus Core Constant datatype, \newline
    \url{https://github.com/input-output-hk/plutus/blob/a04c5681c695c85035958c79bae46130cdd9778e/language-plutus-core/src/Language/PlutusCore/Type.hs#L235}.

\bibitem{plutus-core-term}
  Plutus Core Term datatype, \newline
    \url{https://github.com/input-output-hk/plutus/blob/a04c5681c695c85035958c79bae46130cdd9778e/language-plutus-core/src/Language/PlutusCore/Type.hs#L244}.

\bibitem{address-map}
  Wallet API Address Map, \newline
    \url{https://github.com/input-output-hk/plutus/blob/a04c5681c695c85035958c79bae46130cdd9778e/wallet-api/src/Wallet/Emulator/AddressMap.hs#L39}.
